Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-06-01 paper/manuscript.tex
Updates from Overleaf

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/Fig1_dummy.pdf}
    \caption{Thermodynamic cycles}
    \label{fig:fig1}
\end{figure}
\todo[inline, color=green!20]{This secion needs to be expanded and give a good introduction to the theoretical background without going into too much detail.}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/Fig2_dummy.pdf}
    \caption{a) Bad alignment of congeneric series b) good alignment}
    \label{fig:fig1}
\end{figure}

@@

@@

Absolute free energies are typically reported with respect to a specific reference or standard state, which effectively determines the arbitrary point at which the free energy is 0.
The role of the standard state is particularly evident with binding free energies, in which having a reference state allows us to obtain a well-defined partial molar free energy for the reaction
\begin{equation*}
\ce{AB <=> A + B}
\end{equation*}
through the well-known expression derived from the law of mass action
\begin{equation} \label{eq:DGfromKAB}
\Delta G = -RT ~ \text{ln} \left( C^0 K_{AB} \right)  = -RT ~ \text{ln}\left( \frac{C^0 C_{AB}}{C_A C_B} \right) ,
\end{equation}
where $R$ is the gas, $T$ is the temperature, $C_X$ is the equilibrium concentration of the chemical species $X$ in the reaction solvent, and the reference state concentration $C^0$ converts the binding constant $K_{AB}$ into a dimensionless quantity expressed in reference concentration units.
It should be noted that ignoring the term $C^0$ is equivalent to assuming a reference concentration of 1~D$^{-1}$, where D are the units used to express $K_{AB}$, and would thus cause the value of $\Delta G$ to vary with the choice of the units.
Typically, it is convenient to define a standard state at a constant pressure of 1~atm and where each chemical species (i.e., A, B, and AB) in the reaction solvent has a concentration of $C^0$~=~1~M~=~1~molecule/1660~\r{A}$^3$ but do not interact with other molecules of A, B, or AB.

>>>>

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig2/Fig2.pdf}
    \caption{Thermodynamic cycles}
    \label{fig:fig1}
\end{figure}
\todo[inline, color=green!20]{This secion needs to be expanded and give a good introduction to the theoretical background without going into too much detail.}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig3/Fig2_dummy.pdf}
    \caption{a) Bad alignment of congeneric series b) good alignment}
    \label{fig:fig1}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig6/Fig6.pdf}
    \caption{Absolute thermodynamic cycle}
    \label{fig:fig1}
\end{figure}

@@

Absolute free energies are typically reported with respect to a specific reference or standard state, which effectively determines the arbitrary point at which the free energy is 0.
The role of the standard state is particularly evident with binding free energies, in which having a reference state allows us to obtain a well-defined partial molar free energy for the reaction
\begin{equation*}
\ce{AB <=> A + B}
\end{equation*}
through the well-known expression derived from the law of mass action
\begin{equation} \label{eq:DGfromKAB}
\Delta G = -RT ~ \ln \left( C^0 K_{AB} \right)  = -RT ~ \ln\left( \frac{C^0 C_{AB}}{C_A C_B} \right) ,
\end{equation}
where $R$ is the gas, $T$ is the temperature, $C_X$ is the equilibrium concentration of the chemical species $X$ in the reaction solvent, and the reference state concentration $C^0$ converts the binding constant $K_{AB}$ into a dimensionless quantity expressed in reference concentration units.
It should be noted that ignoring the term $C^0$ is equivalent to assuming a reference concentration of 1~D$^{-1}$, where D are the units used to express $K_{AB}$, and would thus cause the value of $\Delta G$ to vary with the choice of the units.
Typically, it is convenient to define a standard state at a constant pressure of 1~atm and where each chemical species (i.e., A, B, and AB) in the reaction solvent has a concentration of $C^0$~=~1~M~=~1~molecule/1660~\r{A}$^3$ but do not interact with other molecules of A, B, or AB.
